curatedMetagenomicData

### 2019-10-05 curatedMetagenomic_NS.Rmd
test

#BiocManager::install("curatedMetagenomicData")
#BiocManager::install("ExperimentHub")
library(ExperimentHub)
library(curatedMetagenomicData)
suppressPackageStartupMessages(library(ExperimentHub))
library(phyloseq)
library(microbiome)

@@

```{r}
# Create mnd variable
# grabs the nationality from phyloseq
test <- get_variable(pseq, "country" )

# check you've installed this library
library(forcats)
table(test)
# this collapses the two varialbes into a new variable AB in this case. The command for multiple changes is fct_collapse(x, AB = c("A","B"), DE = c("D","E"))

# Not used BGD Bangladesh , CAN Canada, CHN, China. DNK denmark, FJI Figi, HUN Hungry, ISL isle of man , MDG, MNG mongolia, PER Iran, RUS RUSSIA,

test <- fct_collapse(test, LOW = c("NOR","SWE","FIN") , MEDIUM = c("ITA","AUT","DEU","GBR","ESP","FRA","LUX","NLD"), HIGH = c("USA") )

#test <- fct_collapse(test, LOW = c("Scandinavia","EasternEurope") , MEDIUM = c("SouthEurope","CentralEurope", "UKIE"), HIGH = c("US") )

# reorder
test <- factor(test, levels = (c("LOW", "MEDIUM", "HIGH")))
levels(test)

# creates a new variable in the phyloseq called mnd
sample_data(pseq)$mnd = test

# checks that it has worked.
get_variable(pseq.subset, "mnd")

>>>>

#BiocManager::install("curatedMetagenomicData")
#BiocManager::install("ExperimentHub")
library(ExperimentHub)
library(curatedMetagenomicData)
suppressPackageStartupMessages(library(ExperimentHub))
library(phyloseq)
library(microbiome)
library(forcats)

@@

```{r}
# Create mnd variable
# grabs the nationality from phyloseq
mnd.country <- get_variable(pseq, "country" )
table(mnd.country)

# this collapses the two varialbes into a new variable AB in this case. The command for multiple changes is fct_collapse(x, AB = c("A","B"), DE = c("D","E"))
# Not used BGD Bangladesh , CAN Canada, CHN, China. DNK denmark, FJI Figi, HUN Hungry, ISL isle of man , MDG, MNG mongolia, PER Iran, RUS RUSSIA,

mnd.country <- fct_collapse(mnd.country, LOW = c("NOR","SWE","FIN") , MEDIUM = c("ITA","AUT","DEU","GBR","ESP","FRA","LUX","NLD"), HIGH = c("USA") )

#mnd.country <- fct_collapse(mnd.country, LOW = c("Scandinavia","EasternEurope") , MEDIUM = c("SouthEurope","CentralEurope", "UKIE"), HIGH = c("US") )

# reorder
mnd.country <- factor(mnd.country, levels = (c("LOW", "MEDIUM", "HIGH")))
levels(mnd.country)

# creates a new variable in the phyloseq called mnd
sample_data(pseq)$mnd = mnd.country

# checks that it has worked.
get_variable(pseq, "mnd")
